Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil

### 2022-12-16 response-reviewers/response-reviewers.tex

\textbf{1)} The editor writes: ``I agree with R2 that the framing of the study
could be improved. You currently cite a number of interesting figures and basic
facts about lynching in Brazil in the start of the conclusion. I think this
would fit better in the introduction. R2 also argues that the reference to the
Blair et al study on greater costs of local violence is imprecise. I am
guessing you mean something along the lines of likely to affect a greater
number directly than terrorism or civil war, which I think is reasonable but
could be said more directly.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}

We have moved the facts about lynchings in Brazil to the Introduction and 
the section now provides more context for our experiments. The
second paragraph of the Introduction now reads as follows (page 02):
``\textit{One of the most serious forms of extrajudicial violence is lynching.
  Lynching can be defined as ``incidents of physical violence committed by
  large numbers of private citizens against one or more individuals accused of
  having committed a ``criminal'' offense, whether or not this violence
  resulted in the death of the victim(s)'' \citep[645]{godoy2004justice}.
  Although lynchings occur in more than one hundred countries in all regions of
  the world \citep{jung2020lynching,smith2019contradictions}, Latin America has
  been particularly affected by a sharp increase in vigilante violence.
  Lynching episodes have been reported in Guatemala, Mexico, Peru, Venezuela
  and other countries in the region \citep{barbara2015vigilantes,
  cruz2019determinants, godoy2004justice}. From 2011 to 2015, Brazil registered
  about 2,500 lynching episodes, and 173 people were killed by angry mobs in
  2015 alone---nearly one execution every two days
  \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
  Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
  Brazil for more than thirty years, these figures are not only the highest in
  the country's history, but among the highest in the world. The people who
participate in lynchings are typically young men, but they also sometimes
include teenage women and girls, elderly women, and even members of the local
police \citep{moura2017linchamentos}.}''

@@

\vspace{.3cm}

\noindent \textbf{Response:}

\begin{quote}

Reviewer 1 raises an important issue. We agree that we had not adequately
explained the scope conditions of our research and have therefore added a new
paragraph to the Conclusion to provide additional context. In that paragraph,
we compare our results with studies on vigilantism in other Latin American
countries and the United States, and we also discuss the role of social norms,
particularly those related to a culture of honor, in shaping attitudes towards
lynching in Brazil. Additionally, we speculate on why race does not seem to
influence individual preferences for lynchings in Brazil.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{hist.pdf}
  \caption{Support for Lynchings - Experiment 2}
  \label{fig:hist}
\end{figure}

We then cross-checked the distribution of responses with the qualitative
evidence we collected for the conjoint experiment, in which participants had to
justify their choices. When we filter our data to only include respondents who
selected zero on the 0-100 scale, we find the following justifications for
their choices (Portuguese version in parentheses):

\begin{itemize}

  \item ``\textit{It is not justified, but I am forced to express my opinion. We have a death here, but it is not justified}.'' (``não se justifica, mas sou obrigado a opinar. temos uma morte. mas não se jutifica'') 
  \item ``\textit{I only chose it because I had to select a case, as stated. But I do not agree with either of the lynchings and I believe that justice should cover the gap that people use as an excuse for such practice}.'' (``escolhi somente pois deveria obrigatoriamente selecionar um caso, como enunciado. mas não concordo com nenhum dos dois linchamentos e acredito que a justiça deveria cobrir a lacuna que as pessoas utilizam como desculpa para tal prática'')
  \item ``\textit{I don't know... I selected one because I had to do so, but I am strongly against lynching. Eye for an eye, tooth for a tooth}.'' (``não sei bem... escolhi porque tinha que escolher, mas sou fortemente contra linchamento. olho por olho, dente por dente'')
  \item ``\textit{First of all, I want to make it clear that I do not condone either of the two cases. I think there should be no lynching, regardless of the crime. In this approach, I think case 2 is much more serious, because the victim is a child and the perpetrator is an adult, unlike in case 1}.'' (``à princípio quero deixar claro que não compactuo com nenhum dos dois casos. acho que não deve haver linchamento, independente do crime. nessa abordagem, acho que o caso 2 é bem mais grave, pois a vítima se trata de uma criança e autor de adulto, diferentemente do caso 1'')
  \item ``\textit{Either of the answers is immoral. Never, under any circumstances, is vigilante justice justified}.'' (``qualquer das respostas é imoral. nunca, em hipótese alguma a justiça pelas próprias mãos é justificada'')

### 2022-12-17 appendix/appendix.Rmd
final edits to revised version
final edits

This appendix contains the `R` code required to replicate the results we present
in "_Vigilantism and Institutions: Understanding Attitudes towards Lynching in
Brazil_". This file also includes the descriptive statistics of our sample, the
average marginal component effects (AMCEs) for our conjoint experiment, and
additional subgroup analyses for the two experiments included in the main
article.

@@

Below are our results when we disaggregate the data by race. We find that they are
almost identical is all dimensions except for offense. Asian respondents are
much less likely to select profiles that contain pickpocketing as a crime.

>>>>

This appendix contains the `R` code required to replicate the results we present
in "_Vigilantism and Institutions: Understanding Attitudes toward Lynching in
Brazil_". This file also includes the descriptive statistics of our sample, the
average marginal component effects (AMCEs) for our conjoint experiment, and
additional subgroup analyses for the two experiments included in the main
article.

@@

Below are our results when we disaggregate the data by race. We find that they are
almost identical in all dimensions except for offense. Asian respondents are
much less likely to select profiles that contain pickpocketing as a crime.

### 2022-12-17 article/article.tex
final edits to revised version
final edits

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J. D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J. Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments. We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington. This study received IRB approval from Brown University in October 2020 (Protocol 2009002803). Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}. We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.}}

@@

% Date
\date{\today}

@@

We invited respondents from all regions of Brazil to participate in our
experiment. Qualtrics recruited 2,406 adult Brazilian citizens between October
30 and December 22, 2020 to take part in our survey experiment.\footnote{Our
ethics statement is available in Section E of the Supplementary Material.} We
included ten questions on demographics and other information that might
influence the results. These include the respondent's age, gender, ethnicity,
level of education, monthly family income, political orientation (left to
right), support for the death penalty, whether they had been victimized in the
last year, their trust in the police, and their trust in the judicial system.
We used these measures to disentangle heterogeneous effects in the main
responses. Descriptive statistics are available in Section B of the
Supplementary Material.

>>>>

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nick Cowen, Daniel J. D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J. Phillips, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments. We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington. This study received IRB approval from Brown University in October 2020 (Protocol 2009002803). Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}. We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.}}

@@

% Date
\date{December 16, 2022}

@@

We invited respondents from all regions of Brazil to participate in our
experiment. Qualtrics recruited 2,406 adult Brazilian citizens between October
30 and December 22, 2020 to take part in our survey experiment.\footnote{Our
ethics statement is available in Section E of the Supplementary Material.} We
included ten questions on demographics and other information that might
influence the results. The covariates are the respondent's age, gender,
ethnicity, level of education, monthly family income, political orientation
(left to right), support for the death penalty, whether they had been victimized
in the last year, their trust in the police, and their trust in the judicial
system. We used these measures to disentangle heterogeneous effects in the main
responses. Descriptive statistics are available in Section B of the
Supplementary Material.
